Pattern matching for\\ $(231,213)$-avoiding permutations

### 2015-01-31 article.tex
ajout : maccro pour les stripes modif : prise en compte de l ajout de la maccro modif : \upstep = a modif : consistence d une permutation avec \pi

@@

%upstep
\newcommand{\ustep}{u}

@@

An \emph{ascent} of a permutation $\pi \in S_n$ is any position 
$1 \leq i < n$ where the following value is bigger than the current one. 
That is, if $\pi = \pi_1\,\pi_2\,\ldots\,\pi_n$, then
$i$ is an ascent if $\pi_i < \pi_{i+1}$.
For example, the permutation 
$3\,4\,5\,2\,1\,6\,$7 has ascents (at positions) $1,2,5,6$.
Similarly, a \emph{descent} is a position 
$1 \leq i < n$ with $\pi_i > \pi_{i+1}$, 
so every $i$ with $1 \leq i < n$ either is an ascent or is a descent of 
$\pi$.
Let $\ustep$ and $\dstep$ denote an ascend and a descend, respectively.
The \emph{stripe} $s_\pi$ of a permutation $\pi \in S_n$ is the word
$s_{\pi,1} s_{\pi,2} \ldots s_{\pi,n-1} \in \{\ustep,\dstep\}^{n-1}$ 
defined by 
$\mathcal{S}_{\pi,i} = \ustep$ if $i$ an ascent in $\pi$ and
$\mathcal{S}_\pi(i) = \dstep$ if $i$ a descent in $\pi$.
For example the stripe of the permutation 
$\pi = 12\,11\,10\,1\,2\,3,4\,9\,8\,5\,6\,7$ 
is 
$s_\pi = \dstep\dstep\dstep\ustep\ustep\ustep\ustep\dstep\dstep\ustep\ustep$.
The stripe $s_\sigma$ is a \emph{pattern} of the strip $s_\pi$
(or $s_\sigma$ \emph{occurs} of the strip $s_\pi$) if $s_\sigma$ occurs in
$s_\pi$ as a subsequence.

% For two permutations $\
% The stripe $s\pi$ of $\pi \in S-n$ is a motif pmotif \in \Perm{m}$ is a motif
% of a stripe of $\ptext \in \Perm{n}$ if and only if there exist an increasing function $\phi : [|\pmotif|] \rightarrow [|\pmotif|]$
% such that : \\
% $\forall i \in [|\pmotif|]$, $\mathcal{S}(\pmotif,i) = \mathcal{S}(\ptext,\phi(i))$\\
% If a stripe $R_2$ is a motif of a stripe $R_1$,
% it means that there exists
% a subsequence of $R_1$ such as
% this sequence is equal to $R_2$.

@@

		\textbf{Lemma  \numl{firstelement} \thenum} If a permutation is in $\Av{n}{}$ 
		then the first element is either
		the minimal or the maximal element.\\

		\textbf{Proof} Suppose that we have
		$p \in \mathcal{S}_{n}$, and
		$p(1) \neq 1 $ and $p(1) \neq n$ then we have either
		$p(1) ... n ... 1$ or $p(1) ... 1 ... n $, either the motif 231 or 213, which is not possible by hypothesis. $\Box$\\

		\textbf{Corollary  \num \thenum} A permutation $p \in \Perm{n}$ is in $\Av{n}{213,231}$ if and only if for $1 \leq i \leq n$, 
		$p[i:]$ start either with the maximal element
		or the minimal element of $p[i:]$.\\

		\textbf{Corollary \numl{stripe} \thenum}  If $p \in \Av{n}{213,231}$ its stripe can be define such as, \\
		$\mathcal{S}(p,i) = \left\{ 
  		\begin{array}{l l}
   			\ustep & \quad \text{if $p(i)$ is the minimal element of $p[i:]$}\\    
   			\dstep & \quad \text{if $p(i)$ is the maximal element of $p[i:]$}\\
	 	\end{array} \right. 
	 	$\\

		\textbf{Lemma \numl{updown}  \thenum} Let $p \in \Av{n}{213,231}$,
		$\forall i,j \in [n]$, 
		$i<j$, 
		if $\mathcal{S}(p,i)=\ustep$
		and $\mathcal{S}(p,j)=\dstep$
		then $p(i)<p(j)$.\\

		In other word, for every index $i$ and $j$ of an (231,213) avoiding permutation p,
		if $i$ is a up step and
		if $j$ is a down step
		then $p(i)<p(j)$.\\

		\textbf{Proof} By induction on the size of the permutation :
		the proposition is true for the permutations $(1,2)$ and $(2,1)$.
		Suppose the proposition true for $\Av{n}{213,231}$.
		Let $p \in \Av{n}{213,231}$, 
		we show that the proposition holds for $p$.
		Let $p'$ be the permutation $p[2:]$.
		$p' \in \Av{n}{213,231}$, so
		every element of $p'$ verify our lemma (by induction).
		We still need to compare the first element with the rest.
		But the first element
		is the maximal (minimal) element of all the permutation 
		(by Lemma \ref{firstelement}).
		Moreover if the first element is the maximal (minimal)
		it will mapped to an down step (up step).
		So the proposition is also true
		for the first element.
		$\Box$\\

		\textbf{Lemma \numl{upup} \thenum} Let $p \in \Av{n}{213,231}$,
		$\forall i,j \in [n]$, 
		$i<j$, 
		if $\mathcal{S}(p,i)=\ustep$
		and $\mathcal{S}(p,j)=\ustep$
		then $p(i)<p(j)$.\\

		In other word, for every index $i$ and $j$ of an (231,213) avoiding permutation p,
		if $i$ is a up step 
		and $j$ is a up step
		and $ i<j$
		then $p(i)<p(j)$.\\

@@

%		\textbf{Proof} By induction on the size of the permutation :
%		the proposition is true for the permutations $(1,2)$ and $(2,1)$.
%		Suppose the proposition true for $\C{n}$.
%		Let $p \in \C{n+1}$, 
%		we show that the proposition holds for $p$.
%		Let $p'$ be the permutation $p[2:]$.
%		$p' \in \C{n}$, so
%		every element of $p'$ verify our lemma (by induction).
%		We still need to compare the first element with the rest.
%		Except that the first element
%		is the maximal (minimal) element of all the permutation 
%		(by Corollary \ref{stripe}).
%		Moreover if the first element is the maximal (minimal)
%		it will mapped to an down step (up step).
%		So the proposition is also true
%		for the first element.
%		$\Box$\\

		\textbf{Lemma \numl{downdown} \thenum}  Let $p \in \Av{n}{213,231}$,
		$\forall i,j \in [n]$,
		$i<j$,
		if $\mathcal{S}(p,i)=\dstep$
		and $\mathcal{S}(p,j)=\dstep$
		then $p(i)>p(j)$.\\

		In other word, for every index $i$ and $j$ of an (231,213) avoiding permutation p,
		if $i$ is a down step
		and $j$ is a down step
		and $ i<j$
		then $p(i)>p(j)$.\\

@@

%		\textbf{Proof} By induction on the size of the permutation :
%		the proposition is true for the permutations $(1,2)$ and $(2,1)$.
%		Suppose the proposition true for $\C{n}$.
%		Let $p \in \C{n+1}$, 
%		we show that the proposition holds for $p$.
%		Let $p'$ be the permutation $p[2:]$.
%		$p' \in \C{n}$, so
%		every element of $p'$ verify our lemma (by induction).
%		We still need to compare the first element with the rest.
%		Except that the first element
%		is the maximal (minimal) element of all the permutation 
%		(by Corollary \ref{stripe}).
%		Moreover if the first element is the maximal (minimal)
%		it will mapped to an down step (up step).
%		So the proposition is also true
%		for the first element.
%		$\Box$\\

@@

		\textbf{Proof} \\
		$\Rightarrow$ Suppose that $\pmotif$ is a motif of $\ptext$
		by subsequence $s$.
		By definition $s$ normalized is equal to
		$\pmotif$ so they have the same stripe.\\ 
		$\Leftarrow$ 
		Let $\ptext$ be a permutation avoiding $(213,231)$, 
		$R_1$ be its stripe, 
		$\pmotif$  be a permutation avoiding $(213,231)$, 
		and $R_2$ its stripe.
		Let $\phi$ be the function
		that match $R_2$ to $R_1$.
		We define $\varphi$ as, 
		$\forall x \in [|\pmotif|-1]$,
		$\varphi(x) = \phi(x)$,
		and $\varphi(|\pmotif|) = \phi(|\pmotif|-1)+1$
		Suppose that $\exists x,y \in [|\pmotif|]$, 
		$\pmotif(x)<\pmotif(y)$ 
		and $\ptext(\varphi(x))>\ptext(\varphi(y))$,
		without lost of generality we can suppose that $x<y$,
		Let see all the case possible that can make this 
		hypothesis possible :
		\begin{itemize}		
			\item if $\pmotif(x)<\pmotif(y)$, 
			$\mathcal{S}(\pmotif,x)=\ustep$ 
			and $\mathcal{S}(\pmotif,y)=\ustep$
			(if x and y are increasing in $\pmotif$),
			then $\mathcal{S}(\ptext,\varphi(x))=\ustep$ and $\mathcal{S}(\ptext,\varphi(y))=\ustep$,
			(the match are also increasing).
			As $x<y$ and as $\varphi$ is an increasing function, 
			$\varphi(x) < \varphi(y)$.
			And thus, by \textbf{Lemma \ref{upup}},
			$\ptext(\varphi(x)) < \ptext(\varphi(y))$ .
			Which contradict our hypothesis,
			so this case is not possible.

			\item if $\pmotif(x)<\pmotif(y)$, 
			$\mathcal{S}(\pmotif,x)=\ustep$ 
			and $\mathcal{S}(\pmotif,y)=\dstep$
			then $\mathcal{S}(\ptext,\varphi(x))=\ustep$ and $\mathcal{S}(\ptext,\varphi(y))=\dstep$,
			As $x<y$ and as $\varphi$ is an increasing function, 
			$\varphi(x) < \varphi(y)$.
			And thus, by \textbf{Lemma \ref{updown}},
			$\ptext(\varphi(x)) < \ptext(\varphi(y))$ .
			Which contradict our hypothesis,
			so this case is not possible.

			\item if $\pmotif(x)>\pmotif(y)$, 
			$\mathcal{S}(\pmotif,x)=\dstep$ 
			and $\mathcal{S}(\pmotif,y)=\dstep$
			then $\mathcal{S}(\ptext,\varphi(x))=\dstep$ and $\mathcal{S}(\ptext,\varphi(y))=\dstep$,
			As $x<y$ and as $\varphi$ is an increasing function, 
			$\varphi(y) < \varphi(x)$.
			And thus, by \textbf{Lemma \ref{downdown}},
			$\ptext(\varphi(y)) > \ptext(\varphi(x))$ .
			Which contradict our hypothesis,
			so this case is not possible.

			\item if $\pmotif(x)>\pmotif(y)$, 
			$\mathcal{S}(\pmotif,x)=\dstep$ 
			and $\mathcal{S}(\pmotif,y)=\ustep$
			then $\mathcal{S}(\ptext,\varphi(x))=\dstep$ and $\mathcal{S}(\ptext,\varphi(y))=\ustep$,
			As $x<y$ and as $\varphi$ is an increasing function, 
			$\varphi(y) < \varphi(x)$.
			And thus, by \textbf{Lemma \ref{updown}},
			$\ptext(\varphi(y)) > \ptext(\varphi(x))$ .
			Which contradict our hypothesis,
			so this case is not possible.$\Box$

			\item If $y = |\pmotif|$ and $x=|\pmotif|-1$,
			Clearly if $\mathcal{S}(\pmotif,x)=\ustep$,
			then $\pmotif(y)-\pmotif(x)>0$ 
			and because we have a match in the ribbon
			$\ptext(\varphi(y))-\ptext(\varphi(x))>0$.
			Same idea goes if $\mathcal{S}(\pmotif,x)=\dstep$.
			So this case is not possible.

			\item if $y = |\pmotif|$ and $x<|\pmotif|-1$,
			if $\mathcal{S}(\pmotif,x)=\ustep$ ie
			$\pmotif(x+1)-\pmotif(x)>0$. Then
			we must have either
			$\pmotif(x)<\pmotif(x+1)<\pmotif(|\pmotif|)$
			or $\pmotif(x)<\pmotif(|\pmotif|)<\pmotif(x+1)$ 
			to avoid $231$ or $213$ in the motif.
			Because we have a match in the stripe
			and what we prove above,
			$\ptext(\varphi(x+1)-\ptext(\varphi(x))>0$.
			But by hypothesis $\ptext(\varphi(|\ptext|))<\ptext(\varphi(x))$,
			so we have either 		
			$\pmotif(|\pmotif|)<\pmotif(x)<\pmotif(x+1)$
			or $\pmotif(|\pmotif|)<\pmotif(x)<\pmotif(x+1)$ 
			which both lead to a $231$ or a $213$ motif
			in the text which is not possible.
			The same idea goes if $\mathcal{S}(\pmotif,x)=\dstep$.

@@

%			\textbf{Proof}
%			The main point is that
%			if we match a up step (down step) element $i_{\pmotif}$ of the motif
%			with an element $i_{\ptext}$ of the text,
%			the optimal way of matching
%			the first previous up step (down step)
%			that appear before an down step (up step)
%			is to choose the
%			maximal (minimal) element possible.
%			Indeed if we do not take
%			the maximal (minimal) element,
%			we may prevent some element
%			in the future matching.\\

@@

			Given a up step (down step) segment $S(s)$,
			if we want to
			match the suffix $s_ns_{s-1}...s_1$
			starting with an up step (down step),
			and given that we know every
			match of $s_{s-1}...s_1$,
			the optimal way of matching
			$s_{s-1}...s_1$
			is to choose the match
			that minimize (maximize)
			the maximal (minimal)
			element of the match
			and that allow a match
			of $s_n$.			
			In other word if we want to match 
			$\pmotif[IMP(s):]$
			with $\ptext[i:]$
			and match $IMP(s)$
			with $i$.
			The optimal way
			of matching
			$\pmotif[IMP(s-1):]$
			is to choose the
			minimal (maximal) element $\ptext(i')$
			such that :
			(1) $\pmotif[IMP(s-1):]$ is matched with $\ptext[i':]$
			and $IMP(s-1)$ is matched with $e$.
			(2) The segment $S(s)$ is matched with $\ptext[i:i'-1]$
			and $IMP(s)$ is matched with $i$.
			(3) Every elements of the match of (2),
			is inferior (superior) to the minimal (maximal) element of the match of (1).
			Indeed when we will 
			match $s_{n+1}s_ns_{s-1}...s_1$
			more element will be available,
			because every matched 
			element of $s_{n+1}$
			must be superior (inferior)
			to every matched element
			of $s_{s-1}...s_1$.\\

@@

						MIN_{i<i'}\{0\} \cup \{i' |\text{ $i'$ such that } & 
						\text{if $\mathcal{S}(\pmotif,IMP(1))=\ustep$}
						\\
						\text{ $LIS(i,i',\ptext(i')) \leq S(1)$}\}&\\

@@

						MAX_{i<i'}\{0\} \cup \{i' |\text{ $i'$ such that } &
						\text{if $\mathcal{S}(\pmotif,IMP(1))=\dstep$} \\
						\text{ $LDS(i,i',\ptext(i')) \leq S(1)$}\}&\\

@@

						MIN \{0\} \cup  I(s,i) & 
						\text{if $\mathcal{S}(\pmotif,IMP(s))=\ustep$}\\

						MAX \{0\} \cup  D(s,i) & 
						\text{if $\mathcal{S}(\pmotif,IMP(s))=\ustep$}\\

@@

			$I(s,i)=\{e|\text{$i<e$ and $LM(s-1,e)\neq 0$}$ \\
			\indent \indent \indent and  $LIS(i,e-1,IMP(s-1)) \leq S(s) \}$ \\

			$D(s,i)=\{e|\text{$i<e$ and $LM(s-1,e)\neq 0$}$ \\
			\indent \indent \indent and  $LDS(i,e-1,IMP(s-1)) \leq S(s) \}$ \\

@@

			In the base case, 
			we are looking for a match for the first segment.
			Each segment is either up step or down step.
			If the segment is an up step (down step)
			we have to find an increasing (decreasing) sequence
			in the text of same size of longest that 
			the size of the segment,
			and to find the optimal solution 
			we must assure that the last element
			of the sequence is minimal (maximal).\\
			For the induction, it is the same idea
			except that we must assure that 
			every element of the sequence is superior 
			to the maximum element of the rest of the match
			or inferior to the minimal element of the rest of the match
			which is given by $LM$ of
			the previous segment.\\

@@

						\bigcup_{j<k}\mathbb{P}_{\bmotif,\ptext,t(j),max}(i+1,k) 
							& \text{if $\mathcal{S}(\pmotif,i)=\ustep$
							and $i \notin \x$}\\
							& \text{and $i \notin \y$ }\\
							& \text{and $min<\ptext(j)<max$} \\
						&\\

						\bigcup_{j<k}\mathbb{P}_{\bmotif,\ptext,min,t(j)}(i+1,k) 
							& \text{if $\mathcal{S}(\pmotif,i)=\dstep$}\\
							& \text{and $i \notin \x$ and $i \notin \y$  }\\
							& \text{and $min<\ptext(j)<max$} \\		
						&\\

						\mathbb{P}_{\bmotif,\ptext,t(j),max}(i+1,j+1) 
							& \text{if $\mathcal{S}(\pmotif,i)=\ustep$}\\
							& \text{and $i \in \x$ and $i \notin \y$}\\
							& \text{and $min<\ptext(j)<max$} \\
						&\\

						\mathbb{P}_{\bmotif,\ptext,min,t(j)}(i+1,j+1) 
							& \text{if $\mathcal{S}(\pmotif,i)=\dstep$}\\
							& \text{and $i \in \x$ and $i \notin \y$ }\\
							& \text{and $min<\ptext(j)<max$} \\

@@

						\mathbb{P}_{\bmotif,\ptext,t(j),max}(i+1,\ptext^{-1}(\ptext(j)+1)) 
							&\text{if $\mathcal{S}(\pmotif,i)=\ustep$}\\
							&\text{and $i \notin \x$ and $i \in \y$}\\
							& \text{and $min<\ptext(j)<max$} \\
							&\text{and $\ptext^{-1}(\ptext(j)+1)>j$}\\
						&\\

>>>>

%Stripe
\DeclareMathOperator{\stripea}{s}
\newcommand{\stripe}[2]{\stripea_{{#1}}({#2})}
\newcommand{\stripew}[1]{\stripea_{{#1}}}

@@

%upstep
\newcommand{\ustep}{a}

@@

An \emph{ascent} of a permutation $\pi \in S_n$ is any position 
$1 \leq i < n$ where the following value is bigger than the current one. 
That is, if $\pi = \pi_1\,\pi_2\,\ldots\,\pi_n$, then
$i$ is an ascent if $\pi_i < \pi_{i+1}$.
For example, the permutation 
$3\,4\,5\,2\,1\,6\,$7 has ascents (at positions) $1,2,5,6$.
Similarly, a \emph{descent} is a position 
$1 \leq i < n$ with $\pi_i > \pi_{i+1}$, 
so every $i$ with $1 \leq i < n$ either is an ascent or is a descent of 
$\pi$.
Let $\ustep$ and $\dstep$ denote an ascend and a descend, respectively.
The \emph{stripe} $s_\pi$ of a permutation $\pi \in S_n$ is the word
$\stripe{\pi}{1} \stripe{\pi}{2} \ldots \stripe{\pi}{n-1} \in \{\ustep,\dstep\}^{n-1}$ 
defined by 
$ \stripe{\pi}{i}= \ustep$ if $i$ an ascent in $\pi$ and
$\stripe{\pi}{i} = \dstep$ if $i$ a descent in $\pi$.
For example the stripe of the permutation 
$\pi = 12\,11\,10\,1\,2\,3,4\,9\,8\,5\,6\,7$ 
is 
$\stripew{\pi} = \dstep\dstep\dstep\ustep\ustep\ustep\ustep\dstep\dstep\ustep\ustep$.
The stripe $s\stripew{\sigma}$ is a \emph{pattern} of the strip $\stripew{\pi}$
(or $s\stripew{\sigma}$ \emph{occurs} of the strip $\stripew{\pi}$) if $\stripew{\sigma}$ occurs in
$\stripew{\pi}$ as a subsequence.

% For two permutations $\
% The stripe $s\pi$ of $\pi \in S-n$ is a motif pmotif \in \Perm{m}$ is a motif
% of a stripe of $\ptext \in \Perm{n}$ if and only if there exist an increasing function $\phi : [|\pmotif|] \rightarrow [|\pmotif|]$
% such that : \\
% $\forall i \in [|\pmotif|]$, $\mathcal{S}(\pmotif,i) = \mathcal{S}(\ptext,\phi(i))$\\
% If a stripe $S_2$ is a motif of a stripe $S_1$,
% it means that there exists
% a subsequence of $S_1$ such as
% this sequence is equal to $S_2$.

@@

		\textbf{Lemma  \numl{firstelement} \thenum} If a permutation is in $\Av{n}{213,231}$ 
		then the first element is either
		the minimal or the maximal element.\\

		\textbf{Proof} Suppose that we have
		$\pi \in \mathcal{S}_{n}$, and
		$\pi(1) \neq 1 $ and $\pi(1) \neq n$ then we have either
		$\pi(1) ... n ... 1$ or $\pi(1) ... 1 ... n $, either the motif 231 or 213, which is not possible by hypothesis. $\Box$\\

		\textbf{Corollary  \num \thenum} A permutation $\pi \in \Perm{n}$ is in $\Av{n}{213,231}$ if and only if for $1 \leq i \leq n$, 
		$\pi[i:]$ start either with the maximal element
		or the minimal element of $\pi[i:]$.\\

		\textbf{Corollary \numl{stripe} \thenum}  If $\pi \in \Av{n}{213,231}$ its stripe can be define such as, \\
		$\stripe{\pi}{i} = \left\{ 
  		\begin{array}{l l}
   			\ustep & \quad \text{if $\pi(i)$ is the minimal element of $\pi[i:]$}\\    
   			\dstep & \quad \text{if $\pi(i)$ is the maximal element of $\pi[i:]$}\\
	 	\end{array} \right. 
	 	$\\

		\textbf{Lemma \numl{updown}  \thenum} Let $\pi \in \Av{n}{213,231}$,
		$\forall i,j \in [n]$, 
		$i<j$, 
		if $\stripe{\pi}{i}=\ustep$
		and $\stripe{\pi}{j}=\dstep$
		then $\pi(i)<\pi(j)$.\\

		In other word, for every index $i$ and $j$ of an (231,213) avoiding permutation $\pi$,
		if $i$ is an ascent and
		if $j$ is a descent
		then $\pi(i)<\pi(j)$.\\

		\textbf{Proof} By induction on the size of the permutation :
		the proposition is true for the permutations $(1,2)$ and $(2,1)$.
		Suppose the proposition true for $\Av{n}{213,231}$.
		Let $\pi \in \Av{n}{213,231}$, 
		we show that the proposition holds for $\pi$.
		Let $\pi'$ be the permutation $\pi[2:]$.
		$\pi' \in \Av{n}{213,231}$, so
		every element of $p'$ verify our lemma (by induction).
		We still need to compare the first element with the rest.
		But the first element
		is the maximal (minimal) element of all the permutation 
		(by Lemma \ref{firstelement}).
		Moreover if the first element is the maximal (minimal)
		it will mapped to an descent (ascent).
		So the proposition is also true
		for the first element.
		$\Box$\\

		\textbf{Lemma \numl{upup} \thenum} Let $\pi \in \Av{n}{213,231}$,
		$\forall i,j \in [n]$, 
		$i<j$, 
		if $\stripe{\pi}{i}=\ustep$
		and $\stripe{\pi}{j}=\ustep$
		then $\pi(i)<\pi(j)$.\\

		In other word, for every index $i$ and $j$ of an (231,213) avoiding permutation $\pi$,
		if $i$ is a ascent
		and $j$ is a ascent
		and $ i<j$
		then $p(i)<p(j)$.\\

@@

%		\textbf{Proof} By induction on the size of the permutation :
%		the proposition is true for the permutations $(1,2)$ and $(2,1)$.
%		Suppose the proposition true for $\C{n}$.
%		Let $p \in \C{n+1}$, 
%		we show that the proposition holds for $p$.
%		Let $p'$ be the permutation $p[2:]$.
%		$p' \in \C{n}$, so
%		every element of $p'$ verify our lemma (by induction).
%		We still need to compare the first element with the rest.
%		Except that the first element
%		is the maximal (minimal) element of all the permutation 
%		(by Corollary \ref{stripe}).
%		Moreover if the first element is the maximal (minimal)
%		it will mapped to an descent (\pi_2).
%		So the proposition is also true
%		for the first element.
%		$\Box$\\

		\textbf{Lemma \numl{downdown} \thenum}  Let $\pi \in \Av{n}{213,231}$,
		$\forall i,j \in [n]$,
		$i<j$,
		if $\stripe{\pi}{i}=\dstep$
		and $\stripe{\pi}{j}=\dstep$
		then $\pi(i)>\pi(j)$.\\

		In other word, for every index $i$ and $j$ of an (231,213) avoiding permutation $\pi$,
		if $i$ is a descent
		and $j$ is a descent
		and $ i<j$
		then $\pi(i)>\pi(j)$.\\

@@

%		\textbf{Proof} By induction on the size of the permutation :
%		the proposition is true for the permutations $(1,2)$ and $(2,1)$.
%		Suppose the proposition true for $\C{n}$.
%		Let $p \in \C{n+1}$, 
%		we show that the proposition holds for $p$.
%		Let $p'$ be the permutation $p[2:]$.
%		$p' \in \C{n}$, so
%		every element of $p'$ verify our lemma (by induction).
%		We still need to compare the first element with the rest.
%		Except that the first element
%		is the maximal (minimal) element of all the permutation 
%		(by Corollary \ref{stripe}).
%		Moreover if the first element is the maximal (minimal)
%		it will mapped to an descent (ascent).
%		So the proposition is also true
%		for the first element.
%		$\Box$\\

@@

		\textbf{Proof} \\
		$\Rightarrow$ Suppose that $\pmotif$ is a motif of $\ptext$
		by subsequence $s$.
		By definition $s$ normalized is equal to
		$\pmotif$ so they have the same stripe.\\ 
		$\Leftarrow$ 
		Let $\ptext$ be a permutation avoiding $(213,231)$, 
		$S_1$ be its stripe, 
		$\pmotif$  be a permutation avoiding $(213,231)$, 
		and $S_2$ its stripe.
		Let $\phi$ be the function
		that match $S_2$ to $S_1$.
		We define $\varphi$ as, 
		$\forall x \in [|\pmotif|-1]$,
		$\varphi(x) = \phi(x)$,
		and $\varphi(|\pmotif|) = \phi(|\pmotif|-1)+1$
		Suppose that $\exists x,y \in [|\pmotif|]$, 
		$\pmotif(x)<\pmotif(y)$ 
		and $\ptext(\varphi(x))>\ptext(\varphi(y))$,
		without lost of generality we can suppose that $x<y$,
		Let see all the case possible that can make this 
		hypothesis possible :
		\begin{itemize}		
			\item if $\pmotif(x)<\pmotif(y)$, 
			$\stripe{\pmotif}{x}=\ustep$ 
			and $\stripe{\pmotif}{y}=\ustep$
			(if x and y are increasing in $\pmotif$),
			then $\stripe{\ptext}{\varphi(x)} =\ustep$ and $\stripe{\ptext}{\varphi(y)}=\ustep$,
			(the match are also increasing).
			As $x<y$ and as $\varphi$ is an increasing function, 
			$\varphi(x) < \varphi(y)$.
			And thus, by \textbf{Lemma \ref{upup}},
			$\ptext(\varphi(x)) < \ptext(\varphi(y))$ .
			Which contradict our hypothesis,
			so this case is not possible.

			\item if $\pmotif(x)<\pmotif(y)$, 
			$\stripe{\pmotif}{x}=\ustep$ 
			and $\stripe{\pmotif}{y}=\dstep$
			then $\stripe{\ptext}{\varphi(x)}=\ustep$ and $\stripe{\ptext}{\varphi(y)}=\dstep$,
			As $x<y$ and as $\varphi$ is an increasing function, 
			$\varphi(x) < \varphi(y)$.
			And thus, by \textbf{Lemma \ref{updown}},
			$\ptext(\varphi(x)) < \ptext(\varphi(y))$ .
			Which contradict our hypothesis,
			so this case is not possible.

			\item if $\pmotif(x)>\pmotif(y)$, 
			$\stripe{\pmotif}{x}=\dstep$ 
			and $\stripe{\pmotif}{y}=\dstep$
			then $\stripe{\ptext}{\varphi(x)}=\dstep$ and $\stripe{\ptext}{\varphi(y)}=\dstep$,
			As $x<y$ and as $\varphi$ is an increasing function, 
			$\varphi(y) < \varphi(x)$.
			And thus, by \textbf{Lemma \ref{downdown}},
			$\ptext(\varphi(y)) > \ptext(\varphi(x))$ .
			Which contradict our hypothesis,
			so this case is not possible.

			\item if $\pmotif(x)>\pmotif(y)$, 
			$\stripe{\pmotif}{x}=\dstep$ 
			and $\stripe{\pmotif}{y}=\ustep$
			then $\stripe{\ptext}{\varphi(x)}=\dstep$ and $\stripe{\ptext}{\varphi(y)}=\ustep$,
			As $x<y$ and as $\varphi$ is an increasing function, 
			$\varphi(y) < \varphi(x)$.
			And thus, by \textbf{Lemma \ref{updown}},
			$\ptext(\varphi(y)) > \ptext(\varphi(x))$ .
			Which contradict our hypothesis,
			so this case is not possible.$\Box$

			\item If $y = |\pmotif|$ and $x=|\pmotif|-1$,
			Clearly if $\stripe{\pmotif}{x}=\ustep$,
			then $\pmotif(y)-\pmotif(x)>0$ 
			and because we have a match in the ribbon
			$\ptext(\varphi(y))-\ptext(\varphi(x))>0$.
			Same idea goes if $\stripe{\pmotif}{x}=\dstep$.
			So this case is not possible.

			\item if $y = |\pmotif|$ and $x<|\pmotif|-1$,
			if $\stripe{\pmotif}{x}=\ustep$ ie
			$\pmotif(x+1)-\pmotif(x)>0$. Then
			we must have either
			$\pmotif(x)<\pmotif(x+1)<\pmotif(|\pmotif|)$
			or $\pmotif(x)<\pmotif(|\pmotif|)<\pmotif(x+1)$ 
			to avoid $231$ or $213$ in the motif.
			Because we have a match in the stripe
			and what we prove above,
			$\ptext(\varphi(x+1)-\ptext(\varphi(x))>0$.
			But by hypothesis $\ptext(\varphi(|\ptext|))<\ptext(\varphi(x))$,
			so we have either 		
			$\pmotif(|\pmotif|)<\pmotif(x)<\pmotif(x+1)$
			or $\pmotif(|\pmotif|)<\pmotif(x)<\pmotif(x+1)$ 
			which both lead to a $231$ or a $213$ motif
			in the text which is not possible.
			The same idea goes if $\stripe{\pmotif}{x}=\dstep$.

@@

%			\textbf{Proof}
%			The main point is that
%			if we match a ascnt (descent) element $i_{\pmotif}$ of the motif
%			with an element $i_{\ptext}$ of the text,
%			the optimal way of matching
%			the first previous ascnt (descent)
%			that appear before an descent (ascent)
%			is to choose the
%			maximal (minimal) element possible.
%			Indeed if we do not take
%			the maximal (minimal) element,
%			we may prevent some element
%			in the future matching.\\

@@

			Given a ascent (descent) segment $S(s)$,
			if we want to
			match the suffix $s_ns_{s-1}...s_1$
			starting with an ascent (descent),
			and given that we know every
			match of $s_{s-1}...s_1$,
			the optimal way of matching
			$s_{s-1}...s_1$
			is to choose the match
			that minimize (maximize)
			the maximal (minimal)
			element of the match
			and that allow a match
			of $s_n$.			
			In other word if we want to match 
			$\pmotif[IMP(s):]$
			with $\ptext[i:]$
			and match $IMP(s)$
			with $i$.
			The optimal way
			of matching
			$\pmotif[IMP(s-1):]$
			is to choose the
			minimal (maximal) element $\ptext(i')$
			such that :
			(1) $\pmotif[IMP(s-1):]$ is matched with $\ptext[i':]$
			and $IMP(s-1)$ is matched with $e$.
			(2) The segment $S(s)$ is matched with $\ptext[i:i'-1]$
			and $IMP(s)$ is matched with $i$.
			(3) Every elements of the match of (2),
			is inferior (superior) to the minimal (maximal) element of the match of (1).
			Indeed when we will 
			match $s_{n+1}s_ns_{s-1}...s_1$
			more element will be available,
			because every matched 
			element of $s_{n+1}$
			must be superior (inferior)
			to every matched element
			of $s_{s-1}...s_1$.\\

@@

						MIN_{i<i'}\{0\} \cup \{i' |\text{ $i'$ such that } & 
						\text{if $\stripe{\pmotif}{IMP(1)}=\ustep$}
						\\
						\text{ $LIS(i,i',\ptext(i')) \leq S(1)$}\}&\\

@@

						MAX_{i<i'}\{0\} \cup \{i' |\text{ $i'$ such that } &
						\text{if $\stripe{\pmotif}{IMP(1)}=\dstep$} \\
						\text{ $LDS(i,i',\ptext(i')) \leq S(1)$}\}&\\

@@

						MIN \{0\} \cup  I(s,i) & 
						\text{if $\stripe{\pmotif}{IMP(s)}=\ustep$}\\

						MAX \{0\} \cup  D(s,i) & 
						\text{if $\stripe{\pmotif}{IMP(s)}=\ustep$}\\

@@

			$I(s,i)=\{i'|\text{$i<i'$ and $LM(s-1,i')\neq 0$}$ \\
			\indent \indent \indent and  $LIS(i,i'-1,IMP(s-1)) \leq S(s) \}$ \\

			$D(s,i)=\{i'|\text{$i<i'$ and $LM(s-1,i')\neq 0$}$ \\
			\indent \indent \indent and  $LDS(i,i'-1,IMP(s-1)) \leq S(s) \}$ \\

@@

			In the base case, 
			we are looking for a match for the first segment.
			Each segment is either ascent or descent.
			If the segment is an ascent (descent)
			we have to find an increasing (decreasing) sequence
			in the text of same size of longest that 
			the size of the segment,
			and to find the optimal solution 
			we must assure that the last element
			of the sequence is minimal (maximal).\\
			For the induction, it is the same idea
			except that we must assure that 
			every element of the sequence is superior 
			to the maximum element of the rest of the match
			or inferior to the minimal element of the rest of the match
			which is given by $LM$ of
			the previous segment.\\

@@

						\bigcup_{j<k}\mathbb{P}_{\bmotif,\ptext,\ptext(j),max}(i+1,k) 
							& \text{if $\stripe{\pmotif}{i}=\ustep$
							and $i \notin \x$}\\
							& \text{and $i \notin \y$ }\\
							& \text{and $min<\ptext(j)<max$} \\
						&\\

						\bigcup_{j<k}\mathbb{P}_{\bmotif,\ptext,min,\ptext(j)}(i+1,k) 
							& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
							& \text{and $i \notin \x$ and $i \notin \y$  }\\
							& \text{and $min<\ptext(j)<max$} \\		
						&\\

						\mathbb{P}_{\bmotif,\ptext,t(j),max}(i+1,j+1) 
							& \text{if $\stripe{\pmotif}{i}=\ustep$}\\
							& \text{and $i \in \x$ and $i \notin \y$}\\
							& \text{and $min<\ptext(j)<max$} \\
						&\\

						\mathbb{P}_{\bmotif,\ptext,min,t(j)}(i+1,j+1) 
							& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
							& \text{and $i \in \x$ and $i \notin \y$ }\\
							& \text{and $min<\ptext(j)<max$} \\

@@

						\mathbb{P}_{\bmotif,\ptext,\ptext(j),max}(i+1,\ptext^{-1}(\ptext(j)+1)) 
							&\text{if $\stripe{\pmotif}{i}=\ustep$}\\
							&\text{and $i \notin \x$ and $i \in \y$}\\
							& \text{and $min<\ptext(j)<max$} \\
							&\text{and $\ptext^{-1}(\ptext(j)+1)>j$}\\
						&\\
